---
title: "R Notebook"
output: html_notebook
---
Loading data set
```{r}
library(tidyverse)
movies <- read_csv("Movie_Movies.csv")
actors <- read_csv("Movie_Actors.csv")
writers <- read_csv("Movie_Writer.csv")
genres <- read_csv("Movie_Genres.csv")
additional_ratings <- read_csv("Movie_AdditionalRating.csv")
movies
actors
writers
genres
additional_ratings
```
Top 10 directors
```{r}
summary(additional_ratings)
```
Combine the different movie tables by imdbID
```{r}
rated <- movies %>%
  inner_join(additional_ratings, by = "imdbID") %>% 
  select(Director, imdbRating, RatingSource, Rating, imdbVotes, imdbID) %>%
  distinct()
  
rated
```
Descriptive statistics of movies
```{r}
summary(rated)
```
Add colums for Rotten Tomatoes and Meta Critic ratings
```{r}
rated <- rated %>%
  mutate(RottenTomatoesRating = ifelse(RatingSource == "Rotten Tomatoes", Rating, NA))

rated <- rated %>%
  mutate(MetacriticRating = ifelse(RatingSource == "Metacritic", Rating, NA))

rated
```
Convert Roten Tomatoes and Meta Critic rating to format 0-100
```{r}
rated <- rated %>% mutate(RottenTomatoesRating = substr(RottenTomatoesRating,1,nchar(RottenTomatoesRating)-1))

rated <- rated %>% mutate(MetacriticRating = substr(MetacriticRating,1,nchar(MetacriticRating)-4))

rated
```
Convert ratings to 0-10
```{r}
rated <- rated %>% mutate_at(c('RottenTomatoesRating','MetacriticRating'), ~as.numeric(.)) %>%
  mutate(RottenTomatoesRating = RottenTomatoesRating / 10) %>%
  mutate(MetacriticRating = MetacriticRating / 10)

rated
```
Filter top 10 popular directors byImdb ratings
```{r}
top10 <- movies %>% group_by(Director) %>%
  summarise(IMDBscore = mean(imdbRating, na.rm = TRUE),count = n(), imdbVotes = sum(imdbVotes)) %>%
  arrange(desc(IMDBscore)) %>%
  filter(imdbVotes >= 1000334)

top10 <- slice(top10, 1:10)
top10
```
Filter all the movies from the top directors
```{r}
topdirectors <- movies %>% filter(Director %in% top10$Director)
topdirectors
```
Top directors movie genres
```{r}
topgenres <- topdirectors %>% inner_join(genres, by = "imdbID") %>% distinct()
ggplot(data = topgenres) +
  geom_bar(mapping = aes(x = Director, fill = Genre), position = "dodge")
```
```{r}
#top3 genres
#group by genre, count = n(), order by
topgenres %>% group_by(Genre) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
```
```{r}
ggplot(data = topgenres) +
  geom_bar(mapping = aes(x = Genre, fill = Genre))
```
```{r}
topdirectors %>% group_by(Rated) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
```
```{r}
ggplot(data = topdirectors) +
  geom_bar(mapping = aes(x = Rated, fill = Director))
```
Top directors by country
```{r}
topdirectors %>% group_by(Country) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
```
Writers that work the most with the top directors
```{r}
topwriters <- topdirectors %>% inner_join(writers, by = "imdbID") %>% distinct()
topwriters %>% group_by(Person) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
#ggplot(data = topwriters) +
#  geom_bar(mapping = aes(x = Director, fill = Genre), position = "dodge")
```

```{r}
topwriters %>% group_by(Director,Person) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  rename(Writer = Person)
```